opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-28 chapters/01_introduction.tex
Added polarizationn and detector geometry imperfections

%This includes preferred grain orientation, instrument noise, crystallographic defects, internal stress, background originating from various sources, preferred orientation of the sample, ...

@@

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality. In this way, one can bring the simulated patterns closer to those observed in experiments by more accurately modeling the scattering process. Improving the simulation of data involves accounting for more of the physical effects that influence the scattering process such as preferred grain orientation, variations in grain size, crystal defects, the impact of temperature on the scattering process, internal stress, and X-ray-induced fluorescence. \cite{cao2024simxrd} Additionally, it should be considered that varying experimental setups can produce distinct powder diffraction patterns on the same sample. Features that may vary between experimental setups include the shape of diffraction peaks and the employed X-ray source. Some experimental setups may also exhibit imperfections such as displacement of the sample from its intended position leading to the recorded scattering angles being slightly erroneous or background events originating from instrument noise or  X-rays scattering off equipment onto the screen.\\

% Polarizaiton and detector geometry

>>>>

@@

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality. In this way, one can bring the simulated patterns closer to those observed in experiments by more accurately modeling the scattering process. Improving the simulation of data involves accounting for more of the physical effects that influence the scattering process such as preferred grain orientation, variations in grain size, crystal defects, the impact of temperature on the scattering process, internal stress, and X-ray-induced fluorescence. \cite{cao2024simxrd} Additionally, it should be considered that varying experimental setups can produce distinct powder diffraction patterns on the same sample. Features that may vary between experimental setups and influence the recorded pattern include the shape of diffraction peaks, the wavelength and polarization of the employed X-ray source, and the detector geometry. Some experimental setups may also exhibit imperfections such as displacement of the sample from its intended position leading to the recorded scattering angles being slightly erroneous or background events originating from instrument noise or  X-rays scattering off equipment onto the screen.\\
